Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-06-03 background.tex
2015.06.03 (Mema & Vassilis) Mema's latest pass. Also added paper for citation LCCLS2002.

{\sl Napster} was the most successful incarnation of the
centralized approach in file-sharing~\cite{napster}.
It maintained a \emph{central index server} based on file-lists 
that were peer-provided.
Users would query the index server that would ultimately 
yield pointers to the actual content.
Thus, by centralizing search while distributing downloads,  {\sl Napster}
achieved a highly functional design that, at its height, attracted $26$ million
users sharing approximately $80$ million songs\cite{jmm_naptopusage_2001}.
%%
The central indexing component played a vital role in the demise of 
{\sl Napter}, as the \emph{Recording
Industry Association of America} successfully argued in court that this software
entity was enabling copyright infringement of the artists' songs exchanged
through the system.

Architectures that distributed both search and resource provision 
capabilities (Figure~\ref{figure:p2p-archs:unstructred-full}) soon followed.
In these \emph{decentralized} approaches, 
resource placement within the overlay topology is random~\cite{YG-M2002};
for this reason, such architectures are referred to as \emph{unstructured}. 
Key properties of such \p\ systems are that they support inherent heterogeneity
of peers, are highly resilient to peer failures, and incur low maintenance
overhead at handling the dynamics of peer participation
\cite{stutzbach_churn_2006}. 
Unstructured systems are also known as 
\emph{broadcast-based} systems for they use message flooding among %% it is FOR!
peers to propagate search queries. 
In its first realization,
{\sl Gnutella}(\emph{v.0.4}) became a well-known example of the fully
decentralized unstructured approach.

@@

\emph{Decentralized structured schemes} were introduced as an answer to the above
problems of decentralized unstructured \p--approaches
(Figure~\ref{figure:p2p-archs:structured}).
Here, the main objective was to offer 
a self-organizing infrastructure for large-scale \p\ applications
\cite{ratnasamy_can_2001,stoica_chord_2001,antony_pastry_2001,zhao_tapestry_2001,maymounkov_kademlia_2002,rgrk_bamboo_2004}.
To achieve that, they implement a \emph{Distributed Hash Table (DHT)} that maps
objects to nodes through a deterministic mechanism. \emph{DHT}s provide a
guaranteed bound on the number of overlay routing hops that have to be
``traveled'' to locate a resource, even in the case when only a \emph{single}
copy exists within the system. This requires
$O$($log(n)$) hops, compared to the unstructured networks that require
$O(n)$ to reliably locate any object. Unfortunately this efficiency does not
come without cost. Structured overlays can only support exact-match queries 
(i.e., queries that identify resources by name) as opposed
to content-based retrieval provided by unstructured overlays. 
This means that unstructured overlays can support more versatile 
resource location queries such as keyword and partial matching searches. 
Several popular file-sharing \p\ applications have been based on \emph{DHT}s
including {\sl Overnet}/{\sl eDonkey}~\cite{overnet}, 
{\sl Kademlia}/{\sl Kad Network}~\cite{maymounkov_kademlia_2002},  and 
some flavors of {\sl BitTorrent}~\cite{c_bittorrent_2003}.  
Moreover, \emph{DHT}s sparked
a flurry of research for many, diverse, applications ranging
from distributed search engines to event-notification and cloud-based
platforms~\cite{kbc_oceanstore_2000,rkcd_scribe_2001,mgpj_cloudsnap_2011}.

@@

One of the major issues that defines the efficiency of 
an overlay network is its mapping to 
the underlying physical infrastructure. 
Recall, in Figure~\ref{figure:overlay} nodes $A$ and $B$ are 
on the same local network, while $C$ and $D$ are in different networks. 
The top layer represents the overlay interconnection formed by 
these four nodes at a higher level. 
Link connections there, can change as needed by 
the running environment, without any
particular constraint by the underlying physical topology. 
%%
For instance, assume nodes $A$, $B$, $C$ and $D$ being 
connected via the physical network shown in Figure~\ref{figure:phys}
in which costs are depicted in milliseconds. 
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.36]{img/pdf/example-physical.pdf}
\caption{Interconnection of nodes in the physical level.}
\label{figure:phys}
\end{figure}
%%
When peer $A$ sends a message its $D$ counterpart
and depending on the overlay configuration, 
nodes will experience different performance.
For example, in the overlay depicted in
Figure~\ref{figure:overlay-1}, the
message will traverse the following sequence of links in the physical layer
(marked with their costs): $3 \rightarrow 7 \rightarrow 1 \rightarrow 2
\rightarrow 2 \rightarrow 1 \rightarrow 7 \rightarrow 8 \rightarrow 5
\rightarrow 5 \rightarrow 4$. In the alternative overlay of
Figure~\ref{figure:overlay-2}, the path will be: $3 \rightarrow 8 \rightarrow
4$. 
The respective costs are $45 ms$ and $15 ms$.
Evidently, the second overlay is more
congruent with the underlying physical network in comparison 
to the first and, thus, is more efficient.

@@

Early overlay protocol implementations did not pay much attention to map
optimally to the underlying network topology. {\sl Gnutella}, for example, is
considered far from scalable~\cite{ritter_gnucantscale_2001} for every peer
chooses its neighbors without any knowledge of the underlying
network, resulting in mismatches. 
Queries are flooded over multiple paths in an effort 
to reach the node(s) having the sought content. 
In addition, 
pairs of nodes may simultaneously forward the same query to each other
in a superfluous mode of operation in 
this opportunistic and without coordination environment.
%%
\cite{matei_mapgnutella_2002} showed that, even when $95$\% of any two nodes 
are less than $7$ hops away from each other, 
a \emph{flooding-based} {\sl Gnutella}-like algorithm 
can generate $330$TB/month traffic in a $50,000$ node network. 
A topology mismatch can thus have a serious effect 
on Internet's routing performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation and Goal for this Survey}
\label{background:motivation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A topology--unaware overlay network is able to control the sequence of peers a
message traverses before reaching its destination, but it completely ignores
how the actual packets are switched at the underlying infrastructure along
the overlay path. 
In particular, a single logical point-to-point link on the
overlay typically corresponds to multiple physical links in the
underlying layer. 
Moreover, a link in the physical network often lies
on several overlay paths inadvertently increasing the traffic on that
link; this is known as the link's \emph{stress}~\cite{CRSZ2002}. 
There is also the stochastic phenomenon during which peers 
depart and others arrive in the network, known 
as \emph{churn}~\cite{stutzbach_churn_2006}.
Even when an approach offers the best possible location
when a node joins in, the churn is set to  
continuously undermine the effort to maintain the best possible position
of the  peer in the network.

@@

For the \emph{overhead} criterion, we evaluate the cost
of computing and communicating peer join, message forwarding, 
and overlay topology maintenance. For instance, the overhead that an algorithm,
which needs global knowledge of the overlay topology, imposes to the system is
greater compared to a protocol that only relies on peers exchanging routing
tables within a 2-hop radius from each other.

For the \emph{scalability} criterion, we consider system behavior with respect
to the number of participating peers it can reliably support. We characterize
protocols as being lowly, mediumly or highly scalable if they are proven to
effectively support hundreds, tenths of thousands or millions of nodes,
respectively.

>>>>

{\sl Napster} was the most successful incarnation of the
centralized approach in file-sharing~\cite{napster}.
It maintained a \emph{central index server} based on file-lists 
that were peer-provided.
Users would query the index server that would provide 
pointers to the actual content.
Thus, by centralizing search while distributing downloads,  {\sl Napster}
achieved a highly efficient design that, at its height, attracted $26$ million
users sharing approximately $80$ million songs\cite{jmm_naptopusage_2001}.
%%
The central indexing component played a vital role in the demise of 
{\sl Napter}, as the \emph{Recording
Industry Association of America} successfully argued in court that this software
entity was enabling copyright infringement of the artists' songs exchanged
through the system.

Architectures that distributed both search and resource provision 
capabilities (Figure~\ref{figure:p2p-archs:unstructred-full}) soon followed.
In these \emph{decentralized} approaches, 
resource placement within the overlay topology is random~\cite{YG-M2002};
for this reason, such architectures are referred to as \emph{unstructured}. 
Key properties of such \p\ systems are that they support the inherent heterogeneity
of peers, are highly resilient to peer failures, and incur low maintenance
overhead while handling the dynamics of peer participation
\cite{stutzbach_churn_2006}. 
Unstructured systems are also known as 
\emph{broadcast-based} systems for they use message flooding among %% it is FOR!
peers to propagate search queries. 
In its first realization,
{\sl Gnutella}(\emph{v.0.4}) became a well-known example of the fully
decentralized unstructured approach.

@@

\emph{Decentralized structured schemes} were introduced as an answer to the above
problems of decentralized unstructured \p--approaches
(Figure~\ref{figure:p2p-archs:structured}).
Here, the main objective is to offer 
a self-organizing infrastructure for large-scale \p\ applications
\cite{ratnasamy_can_2001,stoica_chord_2001,antony_pastry_2001,zhao_tapestry_2001,maymounkov_kademlia_2002,rgrk_bamboo_2004}.
To achieve this, they implement a \emph{Distributed Hash Table (DHT)} that maps
objects to nodes through a deterministic mechanism. \emph{DHT}s provide a
guaranteed bound on the number of overlay routing hops that have to be
``traveled'' to locate a resource, even in the case when only a \emph{single}
copy exists within the system. This requires
$O$($log(n)$) hops, compared to the unstructured networks that require
$O(n)$ to reliably locate any object. Unfortunately this efficiency does not
come without cost. Structured overlays can only support exact-match queries 
(i.e., queries that identify resources by name) as opposed
to content-based retrieval provided by unstructured overlays. 
This means that unstructured overlays can support more versatile 
resource location queries such as keyword and partial matching searches. 
Several popular file-sharing \p\ applications have been based on \emph{DHT}s
including {\sl Overnet}/{\sl eDonkey}~\cite{overnet}, 
{\sl Kademlia}/{\sl Kad Network}~\cite{maymounkov_kademlia_2002},  and 
some flavors of {\sl BitTorrent}~\cite{c_bittorrent_2003}.  
Moreover, \emph{DHT}s sparked
a flurry of research for many diverse applications, ranging
from distributed search engines to event-notification and cloud-based
platforms~\cite{kbc_oceanstore_2000,rkcd_scribe_2001,mgpj_cloudsnap_2011}.

@@

One of the major issues that defines the efficiency of 
an overlay network is its mapping to 
the underlying physical infrastructure. 
Recall, in Figure~\ref{figure:overlay} nodes $A$ and $B$ are 
on the same local network, while $C$ and $D$ are in different networks. 
The top layer represents the overlay interconnection formed by 
these four nodes at a higher level. 
Link connections there, can change as needed by 
the running environment, without any
particular constraint by the underlying physical topology. 
%%
For instance, assume nodes $A$, $B$, $C$ and $D$ are 
connected via the physical network shown in Figure~\ref{figure:phys}
in which costs are depicted in milliseconds. 
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.36]{img/pdf/example-physical.pdf}
\caption{Interconnection of nodes in the physical level.}
\label{figure:phys}
\end{figure}
%%
When peer $A$ sends a message to peer $D$, 
depending on the overlay configuration, 
nodes will experience different performance.
For example, in the overlay depicted in
Figure~\ref{figure:overlay-1}, the
message will traverse the following sequence of links in the physical layer
(marked with their costs): $3 \rightarrow 7 \rightarrow 1 \rightarrow 2
\rightarrow 2 \rightarrow 1 \rightarrow 7 \rightarrow 8 \rightarrow 5
\rightarrow 5 \rightarrow 4$. In the alternative overlay of
Figure~\ref{figure:overlay-2}, the path will be: $3 \rightarrow 8 \rightarrow
4$. 
The respective costs are $45 ms$ and $15 ms$.
Evidently, the second overlay is more
congruent with the underlying physical network in comparison 
to the first and, thus, is more efficient.

@@

Early overlay protocol implementations gave litte attention to the 
topology mismatch problem.
{\sl Gnutella}, for example, is
considered far from scalable~\cite{ritter_gnucantscale_2001} for every peer
chooses its neighbors without any knowledge of the underlying
network, resulting in mismatches. 
Queries are flooded over multiple paths in an effort 
to reach nodes that have the sought content. 
In addition, 
pairs of nodes may simultaneously forward the same query to each other
in a superfluous mode of operation in 
this opportunistic and without coordination environment.
%%
\cite{matei_mapgnutella_2002} showed that, even when $95$\% of any two nodes 
are less than $7$ hops away from each other, 
a \emph{flooding-based} {\sl Gnutella}-like algorithm 
can generate $330$TB/month traffic in a $50,000$ node network. 
A topology mismatch can thus have a serious effect 
on Internet's routing performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation and Goal for this Survey}
\label{background:motivation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A topology--unaware overlay network is able to control the sequence of peers a
message traverses before reaching its destination, but it completely ignores
how the actual packets are switched at the underlying infrastructure along
the overlay path. 
In particular, a single logical point-to-point link on the
overlay typically corresponds to multiple physical links in the
underlying layer. 
Moreover, a link in the physical network often lies
on several overlay paths inadvertently increasing the traffic on that
link; this is known as the link's \emph{stress}~\cite{CRSZ2002}. 
There is also the stochastic phenomenon during which peers 
depart and others arrive in the network, known 
as \emph{churn}~\cite{stutzbach_churn_2006}.
Even when an approach offers the best possible location
when a node joins, churn   
continuously undermines the effort to maintain the best possible position
of the  peer in the network.

@@

For the \emph{overhead} criterion, we evaluate the cost
of computing and communicating peer join, message forwarding, 
and overlay topology maintenance. For instance, the overhead that an algorithm,
which needs global knowledge of the overlay topology, imposes on the system is
greater compared to a protocol that only relies on peers exchanging routing
tables within a 2-hop radius from each other.

For the \emph{scalability} criterion, we consider system behavior with respect
to the number of participating peers it can reliably support. We characterize
protocols as being lowly, mediumly or highly scalable if they are proven to
effectively support hundreds, tenths of thousands, or millions of nodes,
respectively.

### 2015-06-03 conclusion.tex
2015.06.03 (Mema & Vassilis) Mema's latest pass. Also added paper for citation LCCLS2002.

Research and development in applications and systems that follow the 
\p\ architectural paradigm have flourished for more than a decade now.
By and large, such artifacts exploit the loose-coupling and self-organization 
of participating nodes to shape substrates upon which diverse applications 
can run; the latter offer services including, but not limited to, 
distributed naming, 
Internet telephony and video conferencing, 
storage and indexing, 
content and file sharing, 
web crawling and caching, 
event notification and subscribing/publishing.
%%
These services are provided atop the 
best-effort infrastructure of today's Internet 
and they have to effectively deal with an array of key quality attributes that
they may have to offer, such as node availability, robustness,
scalability, load-sharing, quality-of-service and user anonymity.
%%
The difficulty to handle such features effectively, emanates from the fact that
peer nodes operate at the edge of the Internet and no adequate attention 
is paid to the structure of the physical network during the 
network formation at the application-level.
The deviation of the distributed logically-formed overlay from the 
physical network yields suboptimal use of the underlying 
infrastructure and is known as the topology mismatch
problem.

Development of \p--systems and applications
typically involve juggling a set of tradeoffs (e.g.,
choosing higher accuracy at the cost of increased system overhead).
% Computer systems design is typically about juggling a set of tradeoffs (e.g.,
% choosing higher accuracy at the cost of increased system overhead.)  
In surveying more than
a decade's worth of research efforts aimed at solving the topology mismatch
problem in both unstructured and structured \p\ networks, we find this
tussle-of-tradeoffs property to hold.  
With regards to the three criteria we used --efficiency,
overhead, and scalability-- we find that none of the proposed solutions 
is superior to the others on all three fronts.  This is not surprising.
Nonetheless, by
\begin{inparaenum}[\itshape i\upshape)]
  \item presenting an analysis of each of the solutions,
including what distinguishes it from 
others as well as its advantages and disadvantages and 
  \item offering a pictorial
comparison of how each solution fares in regards to others as far as
efficiency, overhead, and scalability are concerned,
\end{inparaenum}
we hope to have provided \p\
developers and researchers with enough insight and perspective;
as they face specific problems, they will be readily able to 
draw the best possible design decisions for their own application
environments.

>>>>

%% Removing after Mema's suggestion
%Research and development in applications and systems that follow the 
%\p\ architectural paradigm have flourished for more than a decade now.
%By and large, such artifacts exploit the loose-coupling and self-organization 
%of participating nodes to shape substrates upon which diverse applications 
%can run; the latter offer services including, but not limited to, 
%distributed naming, 
%Internet telephony and video conferencing, 
%storage and indexing, 
%content and file sharing, 
%web crawling and caching, 
%event notification and subscribing/publishing.
%%%
%These services are provided atop the 
%best-effort infrastructure of today's Internet 
%and they have to effectively deal with an array of key quality attributes that
%they may have to offer, such as node availability, robustness,
%scalability, load-sharing, quality-of-service and user anonymity.
%%%
%The difficulty to handle such features effectively, emanates from the fact that
%peer nodes operate at the edge of the Internet and no adequate attention 
%is paid to the structure of the physical network during the 
%network formation at the application-level.
%The deviation of the distributed logically-formed overlay from the 
%physical network yields suboptimal use of the underlying 
%infrastructure and is known as the topology mismatch
%problem.
%
Development of \p--systems and applications
typically involve juggling a set of tradeoffs (e.g.,
choosing higher accuracy at the cost of increased system overhead).
% Computer systems design is typically about juggling a set of tradeoffs (e.g.,
% choosing higher accuracy at the cost of increased system overhead.)  
In surveying more than
a decade's worth of research efforts aimed at solving the topology mismatch
problem in both unstructured and structured \p\ networks, we find this
tussle-of-tradeoffs property to hold.  
With regards to the three criteria we used --efficiency,
overhead, and scalability-- we find that none of the proposed solutions 
is superior to the others on all three fronts.  This is not surprising.
Nonetheless, by
\begin{inparaenum}[\itshape i\upshape)]
  \item presenting an analysis of each of the solutions,
including what distinguishes it from 
others as well as its advantages and disadvantages and 
  \item offering a pictorial
comparison of how each solution fares with regards to others 
as far as
efficiency, overhead, and scalability are concerned,
\end{inparaenum}
we hope to provide \p\
developers and researchers with enough insight and perspective;
as they face specific problems, they will be readily able to 
draw the best possible design decisions for their applications.

### 2015-06-03 intro.tex
2015.06.03 (Mema & Vassilis) Mema's latest pass. Also added paper for citation LCCLS2002.

\p\ systems are implemented using \emph{overlay networks}. 
An overlay network, is a virtual system of nodes featuring logical interconnects (or links)
created above an existing network; overlays provide an abstraction that
enables the implementation of efficient, fully distributed, application-layer
services such as routing messages to destinations that are not known in advance
or offering QoS guarantees (i.e., in content-distribution) over best effort
infrastructures. Overlay nodes communicate through \emph{virtual connections}
each of which may correspond to a path of possibly many physical links 
in the underlying network.
Figure~\ref{figure:overlay} illustrates a simple four-node overlay constructed
over a wide-area network.
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.45]{img/pdf/under-over-lay.pdf}
\caption{An example overlay network.}
\label{figure:overlay}
\end{figure}

The single key issue that determines the efficiency of an overlay network,
is how well the overlay maps to the underlying network topology on which it
``rests''. 
Consider two nodes\footnote{In \p\ networks,
the participating nodes are typically user-PCs operating at the edge of the
Internet.} that are connected with each other via a path of overlay links.
If the application running on the nodes, generates heavy traffic along
the overlay path, it would be beneficial to
construct the overlay topology in a way that the number of 
underlying IP links between these two nodes is minimized.
Should the overlay network be constructed so that
it does not match the underlying topology well, 
the inherent \emph{topology mismatch} gives two
major problems. 
First, the performance of the application per se, can be
adversely affected since traffic must flow over a larger,
redundant, number of physical hops resulting in poor user experience 
entailing noticeable latencies or jittering. 
%%
Second, other applications running
on the underlying network infrastructure may be adversely affected as well.
Studies have shown that highly popular \p\ applications contribute 
the largest portion of the overall 
Internet traffic~\cite{seroiu_analysiscds_2002,sen_analyzep2ptraffic_2004,krp_ispfear_2005}, with some reporting that more than $60$\% of this traffic 
to be \p-related~\cite{cachelogic,ipoque2009};
it was also projected that this traffic would reach
$7$~\emph{Exabytes}-per-month by $2018$~\cite{CVNI2014}! 
Evidently, this constitutes a major burden for 
Internet Service Providers (ISPs) who must route 
all of this traffic to destinations at the edge of the Internet. 
If the \p\ overlay topology is poorly designed, 
the demand on the Internet's backbone infrastructure may 
substantially increase as traffic might have to flow
``back and forth'' several times between two neighboring ISPs
while trying to travel from the source to its destination node
in the overlay.
Hence, it is critical that \p\ networks be laid out 
in ways that their topology matches, as closely as possible, the 
underlying IP topology.

@@

The main objective of this paper is to offer a comprehensive 
survey of the work carried out in the area
and provide a
taxonomy of the proposed solutions. We point out synergies, as well as
similarities and differences in the published approaches. 
Ultimately, our goal is to help readers sift through 
the voluminous literature, to help them
understand the advantages and disadvantages of each work, and 
to provide them with enough perspective so that 
when the need arises, they are able to
select, amongst the different approaches, the one that is most suitable for
their particular application.
%%
The rest of the paper is organized as follows: 
Section~\ref{section:background} provides background on
overlay architectures including centralized, decentralized-unstructured and
decentralized-structured \p\ systems.
We also formally define the problem of topology mismatch 
and offer the rationale behind our 
evaluation of the techniques discussed in this paper. 
Work in the area was inspired mostly due to the volatile and fully
distributed nature of the decentrilized overlays so we skip
centralized systems and in Sections~\ref{section:unstructured} and~\ref{section:structured}
we outline the surveyed research efforts
for unstructured and structured \p\ overlays, respectively.
Conclusions can be found in Section~\ref{section:conclusion}.

>>>>

\p\ systems are implemented using \emph{overlay networks}. 
An overlay network, is a virtual system of nodes featuring logical interconnects (or links)
created above an existing network; overlays provide an abstraction that
enables the implementation of efficient, fully distributed, application-layer
services such as routing messages to destinations that are not known in advance
or offering QoS guarantees (i.e., in content-distribution) over best-effort
infrastructures. Overlay nodes communicate through \emph{virtual connections}
each of which may correspond to a path of possibly many physical links 
in the underlying network.
Figure~\ref{figure:overlay} illustrates a simple four-node overlay constructed
over a wide-area network.
%%
\begin{figure}[ht]
\centering
  \includegraphics[scale=0.45]{img/pdf/under-over-lay.pdf}
\caption{An example overlay network.}
\label{figure:overlay}
\end{figure}

The single key issue that determines the efficiency of an overlay network,
is how well the overlay maps to the underlying network topology on which it
``rests''. 
Consider two nodes\footnote{In \p\ networks,
the participating nodes are typically user-PCs operating at the edge of the
Internet.} that are connected with each other via a path of overlay links.
If the application running on the nodes, generates heavy traffic along
the overlay path, it would be beneficial to
construct the overlay topology in a way that the number of 
underlying IP links between these two nodes is minimized.
Should the overlay network be constructed so that
it does not match the underlying topology well, 
the inherent \emph{topology mismatch} creates two
major problems. 
First, the performance of the application per se, can be
adversely affected since traffic must flow over a larger,
redundant, number of physical hops resulting in poor user experience 
entailing noticeable latencies or jitter. 
%%
Second, other applications running
on the underlying network infrastructure may be adversely affected as well.
Studies have shown that highly popular \p\ applications contribute 
the largest portion of the overall 
Internet traffic~\cite{seroiu_analysiscds_2002,sen_analyzep2ptraffic_2004,krp_ispfear_2005}, with some reporting that more than $60$\% of this traffic 
to be \p-related~\cite{cachelogic,ipoque2009};
it was also projected that this traffic would reach
$7$~\emph{Exabytes}-per-month by $2018$~\cite{CVNI2014}! 
This constitutes a major burden for 
Internet Service Providers (ISPs) who must route 
all of this traffic to destinations at the edge of the Internet. 
If the \p\ overlay topology is poorly designed, 
the demand on the Internet's backbone infrastructure may 
substantially increase as traffic might have to flow
``back and forth'' several times between two neighboring ISPs
while trying to travel from the source to its destination node
in the overlay.
Hence, it is critical that \p\ networks be laid out 
in ways that their topology matches the underlying IP topology as 
closely as possible.

@@

The main objective of this paper is to offer a comprehensive 
survey of the work carried out in the area
and provide a
taxonomy of the proposed solutions. We point out synergies, as well as
similarities and differences in the published approaches. 
Ultimately, our goal is to help readers sift through 
the voluminous literature, to help them
understand the advantages and disadvantages of each work, and 
to provide them with enough perspective so that 
when the need arises, they are able to
select, amongst the different approaches, the one that is most suitable for
their particular application.
%%
The rest of the paper is organized as follows: 
In Section~\ref{section:background}, we provide background on
overlay architectures including centralized, decentralized-unstructured and
decentralized-structured \p\ systems.
We also formally define the problem of topology mismatch 
and offer the rationale behind our 
evaluation of the techniques discussed in this paper. 
Work in the area was inspired mostly by the volatile and fully
distributed nature of the decentrilized overlays so we skip
centralized systems and in Sections~\ref{section:unstructured} and~\ref{section:structured}
we outline the surveyed research efforts
for unstructured and structured \p\ overlays, respectively.
We conclude in Section~\ref{section:conclusion}.
